|

### 2015-12-09 manuscript/manuscript_pve.Rmd
text edit

---
title: |
  | Chapter 2 
  | Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_thesis.docx
  pdf_document: default
  html_document:
    number_sections: yes

>>>>

---
title: |
  | Chapter 2 
  | Belowground sink limitation alters growth and carbon balance of Eucalyptus seedlings
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_thesis.docx
  pdf_document: default
  html_document:
    number_sections: yes
